Output Summary

### 2023-06-02 03-post-process/output-plots-children/11-noise-term-diags.Rmd
Implement empty_plot()
Color code the noise summary tables
Rather than bold, the color now shows directionality

no_data_plot = function(main = NULL) {
  plot(1,1, xlim = c(-1,1), ylim = c(-1,1), type = "n", xlab = "", ylab = "", xaxt = "n", yaxt = "n", main = main)
  text(0,0, "No Data", font = 3)
}
```

@@

@@

# format the mean values to present in table
# round and make bold if target value not in interval
proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
proc_error_ests$year_mean_mean = ifelse(!proc_error_ests$yr_mean_incl_target, paste0("<b>", proc_error_ests$year_mean_mean, "</b>"), proc_error_ests$year_mean_mean)
proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
proc_error_ests$year_sd_mean = ifelse(!proc_error_ests$yr_sd_incl_target, paste0("<b>", proc_error_ests$year_sd_mean, "</b>"), proc_error_ests$year_sd_mean)
proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
proc_error_ests$diff_mean = ifelse(!proc_error_ests$diff_incl_target, paste0("<b>", proc_error_ests$diff_mean, "</b>"), proc_error_ests$diff_mean)

# drop unneeded columns
proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_sd_mean", "diff_mean")]
```

```{r proc-error-table-fn}
proc_error_table = function(var) {
  out = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
  out[is.na(out)] = ""

  knitr::kable(out, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    collapse_rows(columns = 1:4)
}
```

@@

# format the mean values to present in table
# round and make bold if target value not in interval
obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
obs_error_ests$year_mean_mean = ifelse(!obs_error_ests$yr_mean_incl_target, paste0("<b>", obs_error_ests$year_mean_mean, "</b>"), obs_error_ests$year_mean_mean)
obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
obs_error_ests$year_sd_mean = ifelse(!obs_error_ests$yr_sd_incl_target, paste0("<b>", obs_error_ests$year_sd_mean, "</b>"), obs_error_ests$year_sd_mean)
obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
obs_error_ests$diff_mean = ifelse(!obs_error_ests$diff_incl_target, paste0("<b>", obs_error_ests$diff_mean, "</b>"), obs_error_ests$diff_mean)

# drop unneeded columns
obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_sd_mean", "diff_mean")]
```

```{r obs-error-table-fn}
obs_error_table = function(var) {
  out = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
  out[is.na(out)] = ""
  out$param = stringr::str_replace(out$param, "->", "$\\\\rightarrow$")

  knitr::kable(out, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    collapse_rows(columns = 1:5)
}
```

>>>>

no_data_plot = function(main = NULL) {
  empty_plot(text = "No Data", label_text = main)
}
```

@@

These tables show posterior summary statistics of the time series of noise terms across years (i.e., the values shown on each figure panel).
Cells with color backgrounds indicate that the posterior or the summary statistic did not include the target value in the 95% CRI; red indicates the posterior was higher than the target blue indicates lower than the target.

@@

# function to assign a color to a cell
assign_color = function(x, do, target) {
  cols_use = ifelse(!do | is.na(x), "white", ifelse(x < target, "blue", "red"))
  alpha(unname(cols_use), 0.25)
}

# format the mean values to present in table
# round and make bold if target value not in interval
proc_error_ests$year_mean_mean = round(proc_error_ests$year_mean_mean, 2)
proc_error_ests$year_mean_col = with(proc_error_ests, assign_color(year_mean_mean, !yr_mean_incl_target, 1))
proc_error_ests$year_sd_mean = round(proc_error_ests$year_sd_mean, 2)
proc_error_ests$year_sd_col = with(proc_error_ests, assign_color(year_sd_mean, !yr_sd_incl_target, 1))
proc_error_ests$diff_mean = round(proc_error_ests$diff_mean, 2)
proc_error_ests$diff_col = with(proc_error_ests, assign_color(diff_mean, !diff_incl_target, 0))

# drop unneeded columns
proc_error_ests = proc_error_ests[,c("phase", "param", "pop", "origin", "LH_type","year_mean_mean", "year_mean_col", "year_sd_mean", "year_sd_col", "diff_mean", "diff_col")]
```

```{r proc-error-table-fn}
proc_error_table = function(var) {
  # extract the numbers to display
  out_values = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = var)
  out_values[is.na(out_values)] = ""

  # extract the colors for the cells
  out_colors = reshape2::dcast(proc_error_ests, phase + param + origin + LH_type ~ pop, value.var = stringr::str_replace(var, "_mean$", "_col"))
  out_colors[is.na(out_colors)] = "#FFFFFF80"

  # make the table
  knitr::kable(out_values, "html", col.names = c("Life Phase", "Process", "Origin", "Migratory Type", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "llllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    column_spec(5, background = out_colors[,5]) %>%
    column_spec(6, background = out_colors[,6]) %>%
    column_spec(7, background = out_colors[,7]) %>%
    column_spec(8, background = out_colors[,8]) %>%
    column_spec(9, background = out_colors[,9]) %>%
    collapse_rows(columns = 1:4)
}
```

@@

# function to assign a color to a cell
assign_color = function(x, do, target) {
  cols_use = ifelse(!do | is.na(x), "white", ifelse(x < target, "blue", "red"))
  alpha(unname(cols_use), 0.25)
}

# format the mean values to present in table
# round and make bold if target value not in interval
obs_error_ests$year_mean_mean = round(obs_error_ests$year_mean_mean, 2)
obs_error_ests$year_mean_col = with(obs_error_ests, assign_color(year_mean_mean, !yr_mean_incl_target, 0.5))
obs_error_ests$year_sd_mean = round(obs_error_ests$year_sd_mean, 2)
obs_error_ests$year_sd_col = with(obs_error_ests, assign_color(year_sd_mean, !yr_sd_incl_target, sqrt(1/12)))
obs_error_ests$diff_mean = round(obs_error_ests$diff_mean, 2)
obs_error_ests$diff_col = with(obs_error_ests, assign_color(diff_mean, !diff_incl_target, 0))

# drop unneeded columns
obs_error_ests = obs_error_ests[,c("type", "param", "pop", "origin", "LH_type", "age", "year_mean_mean", "year_mean_col", "year_sd_mean", "year_sd_col", "diff_mean", "diff_col")]
```

```{r obs-error-table-fn}
obs_error_table = function(var) {
 # extract the numbers to display
  out_values = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = var)
  out_values[is.na(out_values)] = ""
  out_values$param = stringr::str_replace(out_values$param, "->", "$\\\\rightarrow$")

  # extract the colors for the cells
  out_colors = reshape2::dcast(obs_error_ests, type + param + origin + LH_type + age ~ pop, value.var = stringr::str_replace(var, "_mean$", "_col"))
  out_colors[is.na(out_colors)] = "#FFFFFF80"

  knitr::kable(out_values, "html", col.names = c("Class", "Type", "Origin", "Migratory Type", "Age-of-Maturity", "CAT", "LOS", "MIN", "UGR", "Combined"), escape = FALSE, align = "lllllccccc") %>%
    kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("condensed")) %>%
    column_spec(6, background = out_colors[,6]) %>%
    column_spec(7, background = out_colors[,7]) %>%
    column_spec(8, background = out_colors[,8]) %>%
    column_spec(9, background = out_colors[,9]) %>%
    column_spec(10, background = out_colors[,10]) %>%
    collapse_rows(columns = 1:5)
}
```
